---
title: boukary_resume
author: Boukary Ouedraogo
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/resume.css', 'css/styles_html.css', 'resume']
    # css: ['css/custom_resume.css', 'css/styles_pdf.css', 'resume']
    # set it to true for a self-contained HTML  page but it'll take longer to render
    self_contained: true
params:
  doctype: "HTML" # "PDF" or "HTML" is automatically updated in update_resume.R 
  pdf_mode:
    value: true

---

```{r include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(datadrivencv)
library(glue)
library(googlesheets4)
library(googledrive)

# ======================================================================
# These variables determine how the the data is loaded and how the exports are
# done.

# Is data stored in google sheets? If no data will be gather from the csvs/
# folder in project
using_googlesheets <- TRUE

# Just the copied URL from the sheet
positions_sheet_loc <- "https://docs.google.com/spreadsheets/d/1nWVIoaKMEIAGD20TZtdtyZUJYn1xpbITwcysS5c0c78/edit#gid=1701420658"

# Is this sheet available for anyone to read? If you're using a private sheet
# set this to false and go to gather_data.R and run the data loading manually
# once to cache authentication
sheet_is_publicly_readable <- TRUE

# Is the goal of this knit to build a document that is exported to PDF? If so
# set this to true to have links turned into footnotes at the end of the
# document
PDF_EXPORT <- TRUE


# A global (gasp) variable that holds all the links that were inserted for
# placement at the end
links <- c()

# ======================================================================
# Now we source two external scripts. One contains functions for building the
# text output and the other loads up our data from either googlesheets or csvs

# Functions for building sections from CSV data
source('functions/parsing_functions.r') 
source('functions/helper_functions.r') 

# Load data for CV/Resume
    source('functions/gather_data.r')

# Now we just need to filter down the position data to include less verbose
# categories and only the entries we have designated for the resume
position_data <- position_data %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('research_positions', 'industry_positions') ~ 'positions', 
      section %in% c('data_science_writings', 'by_me_press') ~ 'writings',
      TRUE ~ section
    )
  ) 
```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================


Contact {#contact}
--------------------------------------------------------------------------------

```{r contactinfo}

# Adjust contact info based on document type - html has link while pdf does not
if(params$doctype == "HTML") {
  glue::glue('
    - <i class="fa fa-map-marked-alt"></i> Courbevoie, France
    - <i class="fa fa-phone"></i> <a href="tel:+33660786682">(+33) 6 60 78 66 82</a>
    - <i class="fa fa-envelope"></i> bo.ouedraogo7@gmail.com
    - <i class="fa fa-globe" aria-hidden="true"></i> [oboukary.github.io](https://oboukary.github.io/)
    - <i class="fa fa-globe" aria-hidden="true"></i> [boukary.rbind.io](https://boukary.rbind.io/fr/)
    - <i class="fa fa-github"></i> [github.com/oboukary](https://github.com/oboukary)
    - <i class="fab fa-linkedin-in"></i> [linkedin.com/oboukary](https://www.linkedin.com/in/oboukary/)
  ')
} 

if(params$doctype == "PDF") {
  glue::glue('
    - <i class="fa fa-map-marked-alt"></i> Courbevoie, France
    - <i class="fa fa-envelope"></i> bo.ouedraogo7<!-- breaking hyplerlink -->@gmail.com
    - <i class="fa fa-globe" aria-hidden="true"></i> oboukary.github.io
    - <i class="fa fa-globe" aria-hidden="true"></i> boukary.rbind.io
    - <i class="fa fa-github"></i> github.com/oboukary
    - <i class="fab fa-linkedin-in"></i> linkedin.com/oboukary
    - <i class="fa fa-phone"></i> (+33) 6 60 78 66 82
  ')
}

```

<i class="fas fa-download"></i> Download [this resume in PDF](https://oboukary.github.io/resume/resume.pdf) or the
[complete version](https://oboukary.github.io/resume/index.pdf).




```{r download}
# if doctype is html add link to download a pdf version

  #cat("[<i class='fas fa-download'></i> Download as a PDF](https://github.com/oboukary/resume/raw/master/boukary_resume.pdf)")


```

<br>


Coding skills {#skills}
--------------------------------------------------------------------------------

```{r codingskills, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skills,"Coding")

```

Software {#software}
--------------------------------------------------------------------------------

```{r software, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skills, "Software")

```

Interests {#Business}
--------------------------------------------------------------------------------

```{r businessSkills, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skills, "Fields of interest")

```








Disclaimer {#disclaimer}
--------------------------------------------------------------------------------


```{r}

# set disclaimer in bottom right corner based on doctype
if(params$doctype == "HTML") {
  glue::glue("
    Made w/ [**pagedown**](https://github.com/rstudio/pagedown).   
    Source code: [**Github repo**](https://github.com/oboukary/resume).
  ")
} 
if(params$doctype == "PDF") {
  glue::glue("
    Made w/ **pagedown::html_resume**
    Code: **github.com/oboukary/resume** 
  ")
}
```


Last updated on `r Sys.Date()`.
<br>
<br>


Main
================================================================================


Boukary Ouedraogo {#title}
--------------------------------------------------------------------------------

### Data Scientist  |  Statistician  |  Economist

Passionate about international development, issues related to poverty, inequality and sustainable development, I am a data enthusiast who enjoys combining big data, artificial intelligence and emerging technologies to solve business problems. With backgrounds in statistics, economics and finance, I am a person with a strong scientific curiosity. 
I am interested in topics related to development of Africa and Burkina Faso in particular, but I am also opened to global challenges.

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r education}
print_section(position_data, 'education')
```



Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r jobs}
print_section(position_data, 'positions')
```






